---
title: "Predicting harassment"
author: "Sarah Inman"
date: "7 July 2020"
output:
  pdf_document: default
  html_document: default
  word_document: default
  extra_dependencies: float
header-includes: \usepackage{booktabs} \usepackage{longtable} \usepackage{array} \usepackage{multirow} \usepackage{dcolumn} \usepackage{rotating}
  \usepackage{wrapfig} \usepackage{float} \floatplacement{table}{H} \maxdeadcycles=200
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=5, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)

```
# Method summary

We report the relationship between likelihood of reporting different types of harassment and covariates.

We include only those in the sewing section, and we drop those in a supervisor position.

We use a linear probability model, and we cluster standard errors by factory.

We show two subsets of the data: one includes all factories with over one observation, and the second includes our three largest factories (factory codes 13, 63 and 90). For the latter sample, we report p values using the wild cluster bootstrap-t, as per Cameron Gelbach Miller 2008. 

```{r, results = 'asis'}

wd <- '~/Insync/sei2112@columbia.edu/Google Drive - Shared with me/Sarah Summer 2020/COVID-19/'
setwd(wd)
source('Code/Pilot/analysis/reports/predictSexualHarassment/predictSexualHarassment.R')

survey2017 <- read.dta13('Data/raw/2017_survey_data/data_NK_2017 (2).dta') 

dat <- cleanDat(survey2017)
  makeSummaryTables(dat)
runModels(dat)

```

